### 2023-02-03 definitions.tex
details

Let $U,V$ be two upward-closed sets given by its set of minimal element and $D,E$ be two downward-closed sets given by its ideal decomposition. All the four  inclusions $U \subseteq V$,  $U \subseteq D$, $D \subseteq U$ and $D \subseteq E$ are decidable provided that the ordering is decidable and sets are recursive.

@@

\begin{theorem}\label{up-down}
The three uniform resilience problems are decidable for WSTS with effective predbasis and $safe=\uparrow safe$ and bad is upward closed or downward closed.
\end{theorem}

@@

Let us examine the uniform $k$-resilience problem (UkRP). we may compute the least $n$ such that $ \uparrow \pred^n(SAFE)=  \uparrow \pred^*(SAFE)$. S is uniformely $k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}and then UkRP is decidable.
\end{proof}

@@

\subsection{Case: $BAD=\downarrow BAD$ and $SAFE=\uparrow SAFE$.}

@@

\subsection{Case: $BAD=\uparrow BAD$ and $SAFE=\uparrow SAFE$.}

@@

\subsection{Case: $BAD=\downarrow BAD$ and $SAFE=\downarrow SAFE$.}

%%%%%%%%
\subsection{Case: $BAD=\uparrow BAD$ and $SAFE=\downarrow SAFE$.}
%
%		cas exclusion mutuelle
%
je prends les minimaux de bad et les idéaux de safe, pas sur que ce soit decidable....$pred(safe)$

>>>>

Let $U,V$ be two upward-closed sets given by its set of minimal element and $D,E$ be two downward-closed sets given by its ideal decomposition. All the four  inclusions $U \subseteq V$,  $U \subseteq D$, $D \subseteq U$ and $D \subseteq E$ are decidable provided that the ordering is decidable and sets are recursive.
%
\alain{on peut penser à des ensembles bad definis dans une logique booleennne sur les clos par le bas, haut, +...}

@@

\begin{theorem}\label{up-down}
The three uniform resilience problems are decidable for WSTS with effective predbasis and $safe=\uparrow safe$.
%	and bad is upward closed or downward closed.
\end{theorem}

@@

Let us examine the uniform $k$-resilience problem (UkRP). we may compute the least $n$ such that $bad \subseteq \uparrow \pred^n(SAFE)=  \uparrow \pred^*(SAFE)$. S is uniformely $k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}and then UkRP is decidable.
\end{proof}

@@

Let us show that the predbasis hypothesis can be replaced by other hypotheses.

\subsection{Case: $SAFE=\uparrow SAFE$ and $BAD=\downarrow BAD$.}

@@

\subsection{Case: $SAFE=\uparrow SAFE$ and $BAD=\uparrow BAD$.}

@@

\subsection{Case: $SAFE=\downarrow SAFE$ and $BAD=\downarrow BAD$.}

%%%%%%%%
\subsection{Case: $SAFE=\downarrow SAFE$ and $BAD=\uparrow BAD$.}
%
%		cas exclusion mutuelle
%
je prends les minimaux de bad et les idéaux de safe, pas sur que ce soit decidable....$pred(safe)$
